Indexing Variation Graphs\footnote{This work was supported by the Wellcome Trust grant [098051].}

### 2016-04-21 paper/paper.tex
Further proofreading.

The \emph{succinct de~Bruijn graphs} of Bowe et.~al.~\cite{Bowe2012} is generalization of the FM\nobreakdash-index as GCSA for representing \emph{de~Bruijn graphs} space-efficiently. Rødland \cite{Roedland2013} proposed another similar generalization. Succinct de~Bruijn graphs can represent \orderk{k} de~Bruijn graphs with different values of $k$ in the same structure \cite{Boucher2014}, but they still need to store the graph for the largest value of $k$ explicitly. Compacted \cite{Cazaux2014} and compressed de~Bruijn graphs \cite{Marcus2014} achieve similar space usage by representing unary paths in the graph as single nodes. A prototype read aligner based on compacted de~Bruijn graphs has been proposed \cite{Limasset2015}.

@@

The proofs of lemmas describing the properties of generalizations of de~Bruijn graphs are included in Appendix~\ref{appendix:proofs}. The other appendices contain more material from the full paper.

@@

\begin{definition}[Path graph]
Let $\mathcal{S}$ be a \kcollection{k} of the labels of maximal paths in graph $G = (V, E)$, and let $\mathcal{K}$ be a prefix-free set of substrings of length $k$ or less from $\mathcal{S}$. Assume that each right-maximal subtring $S \in \mathcal{S}$ prefix-matches a string $K \in \mathcal{K}$, and that $\#^{k}, \$^{k} \in \mathcal{K}$. The \orderk{k} \emph{path graph} of graph $G$ with \emph{key set} $\mathcal{K}$ is a graph $G' = (V', E')$, where
\begin{itemize}
\item each node $v_{K} \in V'$ represent a distinct key $K \in \mathcal{K}$, with $G'.\glabel(v_{K}) = K[0]$;
\item each node has a key $G'.\gkey(v_{K}) = K$ and a value $G'.\gvalue(v_{K}) = V_{K}$, where $V_{K}$ is the set of nodes $\mathcal{S}.\gnode(S, i) \in V$ for $S \in \mathcal{S}$ and positions $i$ such that $S[i, i+\abs{K}-1] = K$; and
\item each edge $(v_{K}, v_{K'}) \in E'$ represents the occurrence of substring $K[0] K'$ in $\mathcal{S}$ such that strings $K$ and $K[0] K'$ prefix-match.
\end{itemize}
We use the node corresponding to $\#^{k}$ as the source node $s$ and the node corresponding to $\$^{k}$ as the sink node $t$, adding the technical edge $(t, s)$ in the usual way.
\end{definition}

>>>>

The \emph{succinct de~Bruijn graphs} of Bowe et.~al.~\cite{Bowe2012} is generalization of the FM\nobreakdash-index for representing \emph{de~Bruijn graphs} space-efficiently. Rødland \cite{Roedland2013} proposed another similar generalization. Succinct de~Bruijn graphs can represent \orderk{k} de~Bruijn graphs with different values of $k$ in the same structure \cite{Boucher2014}, but they still need to store the graph for the largest value of $k$ explicitly. Compacted \cite{Cazaux2014} and compressed de~Bruijn graphs \cite{Marcus2014} achieve similar space usage by representing unary paths in the graph as single nodes. A prototype read aligner based on compacted de~Bruijn graphs has been proposed \cite{Limasset2015}.

@@

The proofs of lemmas describing the properties of generalizations of de~Bruijn graphs are included in Appendix~\ref{appendix:proofs}. The other appendices contain material from the full paper.

@@

\begin{definition}[Path graph]
Let $\mathcal{S}$ be a \kcollection{k} of the labels of maximal paths in graph $G = (V, E)$, and let $\mathcal{K}$ be a prefix-free set of substrings of length $k$ or less from $\mathcal{S}$. Assume that each right-maximal substring $S \in \mathcal{S}$ prefix-matches a string $K \in \mathcal{K}$, and that $\#^{k}, \$^{k} \in \mathcal{K}$. The \orderk{k} \emph{path graph} of graph $G$ with \emph{key set} $\mathcal{K}$ is a graph $G' = (V', E')$, where
\begin{itemize}
\item each node $v_{K} \in V'$ represent a distinct key $K \in \mathcal{K}$, with $G'.\glabel(v_{K}) = K[0]$;
\item each node has a key $G'.\gkey(v_{K}) = K$ and a value $G'.\gvalue(v_{K}) = V_{K}$, where $V_{K}$ is the set of nodes $\mathcal{S}.\gnode(S, i) \in V$ for $S \in \mathcal{S}$ and positions $i$ such that $S[i, i+\abs{K}-1] = K$; and
\item each edge $(v_{K}, v_{K'}) \in E'$ represents the occurrence of substring $K[0] K'$ in $\mathcal{S}$ such that strings $K$ and $K[0] K'$ prefix-match.
\end{itemize}
We use the node corresponding to $\#^{k}$ as the source node $s$ and the node corresponding to $\$^{k}$ as the sink node $t$, adding the technical edge $(t, s)$ in the usual way.
\end{definition}
